Structured Versus Decorated Cospans

### 2020-12-15 cospans.tex
Added a bit about monoidal units at the end of Theorem 3.2

{\chris Kenny, I am a bit confused with all the units and monoidal units around. Could you go through in detail, and phrase correctly, the following part? Following the definition of a monoidal double functors and related structures precisely? For example, shouldn't we start from the monoidal unit of structured cospans? How do you write that?}
Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \one\to F(0_A)\to F(0_A)$,
which is an initial object and as such isomorphic to $0_{F(0)}$
%=\lE((0_A,)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$
again by \cref{eq:explicitstructure2}. It can be verified that with the above structure, $\lE_1$ is also a symmetric monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.
\end{proof}

@@

\begin{defn}\label{defn:monoidal_double_functor}
Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \colon \lD \to \lE$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon 1_\lE \to \lF \circ 1_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
\end{defn}
{\chris Those units in the definition should be monoidal units not unit functors...}
\noindent
Unpacking this definition, one obtains a number of diagrams which can be found after \cite[Definition 2.14]{HS}.

>>>>

{\chris Kenny, I am a bit confused with all the units and monoidal units around. Could you go through in detail, and phrase correctly, the following part? Following the definition of a monoidal double functors and related structures precisely? For example, shouldn't we start from the monoidal unit of structured cospans? How do you write that?}
Moreover, the monoidal unit for the category of arrows of $F\lCsp$ is $0_\A\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}0_\A$ with the trivial decoration $\phi_0\maps \one\to F(0_A)\to F(0_A)$,
which is an initial object and as such isomorphic to $0_{F(0)}$
%=\lE((0_A,)\xrightarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0)\xleftarrow{\raisebox{-3pt}[0pt][0pt]{$=$}}(0_A,\phi_0))$
again by \cref{eq:explicitstructure2}. It can be verified that with the above structure, $\lE_1$ is also a symmetric monoidal functor, and the rest of the axioms of \cref{defn:monoidal_double_functor} hold.

\textbf{Kenny: This is what I would say regarding the monoidal units:} Moreover, the monoidal unit $I_{F\lCsp}$ for the category of arrows of $F\lCsp$ is given by the identity cospan $0_\A \rightarrow 0_\A \leftarrow 0_\A$ on the monoidal unit of $\A$ together with the trivial decoration $\bot_{0_\A} = \phi_0 \colon 1 \to F(0_\A)$ on $0_\A$, and the monoidal unit $I_{{_L \lCsp(\int F)}}$ for the category of arrows of ${ _L \lCsp(\int F)}$ is given by $(0_\A,\bot_{0_\A}) \rightarrow (0_\A,\bot_{0_\A}) \leftarrow (0_\A,\bot_{0_\A})$, with $\lE(I_{{ _L \lCsp(\int F)}})$ also being given by the identity cospan on $0_\A$ with the trivial decoration on its apex so that the transformation $\theta_U \colon I_{F\lCsp} \to \lE \circ I_{{_L \lCsp (\int F)}}$ is an identity.
\end{proof}

@@

\begin{defn}\label{defn:monoidal_double_functor}
Given symmetric monoidal double categories $\lD$ and $\lE$, a \define{symmetric monoidal double functor} $\lF \colon \lD \to \lE$ is a double functor $\lF$ together with transformations $\theta \colon {\otimes \circ (\lF,\lF)} \to \lF \circ \otimes$ and $\theta_U \colon I_\lE \to \lF \circ I_\lD$ that satisfy the usual coherence axioms for a symmetric monoidal functor with respect to $\otimes$.
\end{defn}
{\chris Those units in the definition should be monoidal units not unit functors...}
%%% Kenny: How about I instead of 1?
\noindent
Unpacking this definition, one obtains a number of diagrams which can be found after \cite[Definition 2.14]{HS}.
